Imputation of Incomplete Multilevel Data with R

### 2023-12-22 Manuscript/manuscript.qmd
Re-run on different pc

```{r}
#| label: setup
#| echo: false
#| warning: false
#| message: false
library(knitr)
library(ggplot2)
source("../docs/utils.R")
source("../docs/tables.R")
```

>>>>

```{r}
#| label: setup
#| echo: false
#| warning: false
#| message: false
library(knitr)
library(ggplot2)
source("../Manuscript/utils.R")
source("../Manuscript/tables.R")
```
